Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-09-13 Rdocs/ManuscriptLPP.Rmd
finished all plots!

  #plotting
  ggplot(new_tbl, aes(x = reorder(material, -index, sum), y = index)) +
    geom_col(aes(fill = reorder(material, -index, sum))) +
    geom_errorbar(aes(ymin = index - 2*index_se, ymax = index + 2*index_se)) +
geom_text(aes(y = (index + 2*index_se)+0.05, label =groups)) +

@@

#by material (plastic comparisons only)
ggplot(BC_ByMat_tibble[7:10,], aes(x = mat_comp, y = bc_score, fill = mat_comp)) +geom_col() +
  theme_rafa() + scale_fill_viridis_d()+
  coord_cartesian(ylim = c(0, 1)) +
  labs(title = "Community Dissimilairty between bag types", x = "Material Comparison",
       y = "Bray Curtis Dissimilarity", fill = "Comparisons")

>>>>

  #plotting
  ggplot(new_tbl, aes(x = reorder(material, -index, sum), y = index)) +
    geom_col(aes(fill = reorder(material, -index, sum))) +
    geom_errorbar(aes(ymin = index - 2*index_se, ymax = index + 2*index_se)) +
geom_text(aes(y = (index + 3*index_se), label =groups)) +

@@

#by material (plastic comparisons only)
ggplot(BC_ByMat_tibble[7:10,], aes(x = mat_comp, y = bc_score, fill = mat_comp)) +geom_col() +
  theme_rafa() + scale_fill_viridis_d()+
  coord_cartesian(ylim = c(0, 1)) +
  labs(title = "Community Dissimilarity between plastic and biodegradable bags", x = "Material Comparison",
       y = "Bray Curtis Dissimilarity", fill = "Comparisons")

#NMDS plots----
#extract scores from NMDS object
TC_NMDS_Scores <- as_tibble(scores(taxaCount_NMDS, display = "sites"))
TC_NMDS_Scores$site <- LPP_FullData$site
TC_NMDS_Scores$date <- LPP_FullData$date
TC_NMDS_Scores$material <- LPP_FullData$material

#plotting
ggplot(TC_NMDS_Scores, aes(x = NMDS1, y = NMDS2, fill = material)) +
  geom_hline(yintercept = 0, linetype = 5) + geom_vline(xintercept = 0, linetype = 5) +
  geom_point(shape = 21, size = 2.5) +
  facet_wrap(~date)+
  theme_rafa() +
  labs(title = "Non-Metric Dimensional Scaling of Community Matrices")+
  scale_fill_viridis_d()
```
